Who mistrust basic science?

### 2024-03-25 paper.Rmd
update author info after first study

author: 
  - name          : "Jan Pfänder"
    affiliation   : "1"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Data collection"
      - "Statistical Analyses"
      - "Writing - Original Draft"
      - "Writing - Review & Editing"
  - name          : "Lou Kerzreho"
    affiliation   : "1"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Models and Simulations"
      - "Writing - Review & Editing"
  - name          : "Hugo Mercier"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "hugo.mercier@gmail.com"
    address: " "
    role:
      - "Conceptualization"
      - "Writing - Original Draft"
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Institut Jean Nicod, Département d’études cognitives, ENS, EHESS, PSL University, CNRS, France"
  - id            : "2"
    institution   : "Max Planck Institute for the Study of Crime, Security and Law, Freiburg im Breisgau, Germany"

@@

classoption       : "doc" # "doc" for nice look, "man" for manuscripty
output            : papaja::apa6_doc # "_doc" for word; however, note that some of the features of kableExtra are not available for word and will yield errors. For example to knit to word, you'll have to comment out all "add_header_above()" functions for model output tables, or e.g. set always allow html as true in the yaml heading

@@

(ref:exp1-conditional-acceptance) **A** Shows the distribution of science knowledge (left) and acceptance of scientific consensus  **B** Shows the relationship between trust in science and science knowledge/acceptance of scientific consensus **C** Shows the relationship between conspiracy thinking and science knowledge/acceptance of scientific consensus

>>>>

author: 
  - name          : "Jan Pfänder"
    affiliation   : "1"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)

  - name          : "Lou Kerzreho"
    affiliation   : "1"
    role:

  - name          : "Hugo Mercier"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "hugo.mercier@gmail.com"
    address: " "
    role:

affiliation:
  - id            : "1"
    institution   : "Institut Jean Nicod, Département d’études cognitives, ENS, EHESS, PSL University, CNRS, France"

@@

classoption       : "doc" # "doc" for nice look, "man" for manuscripty
output            : papaja::apa6_pdf # "_doc" for word; however, note that some of the features of kableExtra are not available for word and will yield errors. For example to knit to word, you'll have to comment out all "add_header_above()" functions for model output tables, or e.g. set always allow html as true in the yaml heading

@@

(ref:exp1-conditional-acceptance) Acceptance rates of scientific consensus, based on whether the initial response to the knowledge question was false or true.

### 2024-03-25 paper.tex
update author info after first study

The authors made the following contributions. Jan Pfänder: Conceptualization, Data collection, Statistical Analyses, Writing - Original Draft, Writing - Review \& Editing; Lou Kerzreho: Models and Simulations, Writing - Review \& Editing; Hugo Mercier: Conceptualization, Writing - Original Draft, Writing - Review \& Editing, Supervision.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institut Jean Nicod, Département d'études cognitives, ENS, EHESS, PSL University, CNRS, France\\\textsuperscript{2} Max Planck Institute for the Study of Crime, Security and Law, Freiburg im Breisgau, Germany}

@@

\begin{figure}
\centering
\includegraphics{output/figures/exp1-conditional-acceptance.pdf}
\caption{\label{fig:exp1-conditional-acceptance}\textbf{A} Shows the distribution of science knowledge (left) and acceptance of scientific consensus \textbf{B} Shows the relationship between trust in science and science knowledge/acceptance of scientific consensus \textbf{C} Shows the relationship between conspiracy thinking and science knowledge/acceptance of scientific consensus}
\end{figure}

>>>>

The authors made the following contributions. Jan Pfänder: ; Lou Kerzreho: ; Hugo Mercier: .

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institut Jean Nicod, Département d'études cognitives, ENS, EHESS, PSL University, CNRS, France}

@@

\begin{figure}
\centering
\includegraphics{output/figures/exp1-conditional-acceptance.pdf}
\caption{\label{fig:exp1-conditional-acceptance}Acceptance rates of scientific consensus, based on whether the initial response to the knowledge question was false or true.}
\end{figure}
